### 2023-05-02 inst/publication/Code/fit_models_durations.Rmd
Added AIC variation

```{r, preamble, include = FALSE}
devtools::load_all()

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "DejaVuSerif", size = 48)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("fit_data.R")
library(kableExtra)

library(showtext)
showtext_auto()

@@

all_sites <- as.list(rep(0, 20))
names(all_sites) <- get_data() %>%
  select(site) %>%
  unique() %>%
  pull()
```

@@

```{r}
# set waggle dance duration in seconds as foraging distance for analysis
data <- read.csv("data/FullHBForagingData.csv")

@@

@@

>>>>

```{r, preamble, include = FALSE}
devtools::load_all()
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(ggplot2)
theme_set(
  theme_classic() +
    theme(
      text = element_text(family = "DejaVuSerif", size = 48)
    )
)
library(cowplot)
library(dplyr)
library(tibble)
source("Code/fit_data.R")
library(kableExtra)
print(getwd())
library(showtext)
showtext_auto()

@@

all_sites <- as.list(rep(0, 20))
names(all_sites) <- get_data() %>%
  select(site) %>%
  unique() %>%
  pull()

```

@@

```{r}
# set waggle dance duration in seconds as foraging distance for analysis
data <- read.csv("Data/FullHBForagingData.csv")

@@

### Fits to all urban and all agri-rural sites

```{r, ZSL, message = FALSE, warning = FALSE}
urban_sites <- c("BLO", "BUR", "CAD", "GIL", "HHS", "HOR", "MAK", "MPA", "SWP", "ZSL")
rural_sites <- c("BEL", "BFI", "HER", "MEL", "SAU", "SOM", "SRA", "STU", "YAL") # exclude ROT due to bad fit

urban_data <- alldata %>%
  filter(site %in% urban_sites)

rural_data <- alldata %>%
  filter(site %in% rural_sites)

# urban
all_sites[["urban"]] <- run_wagglefit_analysis(
  "urban", urban_data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[["urban"]]$fit_result %>%
  kbl() %>%
  kable_classic(full_width = F)

# rural
all_sites[["rural"]] <- run_wagglefit_analysis(
  "rural", rural_data, collective_bounds, individual_bounds, subplot_coords
)

all_sites[["rural"]]$fit_result %>%
  kbl() %>%
  kable_classic(full_width = F)

```

@@

```{r, make-aic-comp, message = FALSE, warning = FALSE}
# group all site results together
df <- map(all_sites, 1) %>%
  bind_rows()

all_sites

# filter for best model
sitedata <- df %>%
  group_by(site) %>%
  slice(which.min(AIC))

sitedata$LU <- NA
sitedata2 <- sitedata %>%
  mutate(LU= ifelse(
    site %in% urban_sites, 'Urban',
    ifelse(
      site %in% rural_sites,
      'Rural',
      paste0('Total_', site)
    ))) %>%
  filter(site != 'ROT')

print(sitedata2, n=22)

sitedata2 %>%
  group_by(LU) %>%
  summarise(AIC=sum(AIC))

```

### 2023-05-02 inst/publication/Code/landuse_effect_jackknife.Rmd
Added AIC variation

@@

@@

```{r, urban_jk_outlier_removed, message = FALSE, error = FALSE, warning = FALSE, echo = FALSE}

# full data fit
model_pls <- plsRbeta(
  p_transform ~ .,
  data = urban.pcadata,
  nt = ncol(urban.pcadata) - 1,
  model = "pls-beta",
  verbose = FALSE
)
plsdata <- data.frame(
  prop.scouts = model_pls$dataY,
  pc1 = model_pls$tt[, 1]
)
plsbetamodel <- betareg(
  prop.scouts ~ pc1,
  plsdata
)

@@

plt <- ggplot(data = urban_jk_loadings, aes(
  x = landuse_type, y = loadings, fill = landuse_type
)) +
  geom_point(aes(colour = landuse_type)) +
  geom_segment(aes(
    x = landuse_type, xend = landuse_type,
    y = 0, yend = loadings, colour = landuse_type
  )) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = urban_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -urban_cuttoff,
    ymax = urban_cuttoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text(size = 15),
    strip.text.x = element_text(size = 18),
    axis.title.x = element_text(size = 18)
  ) +
  scale_fill_manual(
    values = c(
      "arable" = "#CCBB44", "built.up.area" = "#EE6677",
      "Non.agricultural.unmanaged.green.space" = "#228833",
      "water" = "#4477AA", other = "#BBBBBB"
    )
  ) +
  facet_wrap(~site_removed, ncol = 2)
ggsave(
  plot = plt,
  filename = "../Results/figures/SI_figures/urban_jk_individual_loadings.png",
  width = 120,
  height = 200,
  units = "mm",
  dpi = 300
)
plt
```

@@

plt <- ggplot(data = rural_jk_loadings, aes(
  x = landuse_type, y = loadings, fill = landuse_type
)) +
  geom_point(aes(colour = landuse_type)) +
  geom_segment(aes(
    x = landuse_type, xend = landuse_type,
    y = 0, yend = loadings, colour = landuse_type
  )) +
  geom_hline(
    yintercept = 0, color = "black"
  ) +
  geom_text(
    data = rural_loading_text,
    aes(x = landuse_type, y = result, label = landuse_type),
    hjust = 0.5,
    vjust = 0.5,
    nudge_y = c(-0., -0.), nudge_x = c(0.5, 0.5)
  ) +
  annotate(
    "rect",
    ymin = -rural_cuttoff,
    ymax = rural_cuttoff,
    xmin = 0, xmax = Inf,
    alpha = 0.2
  ) +
  coord_flip() +
  theme_classic() +
  theme(
    axis.line.y = element_blank(),
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "None",
    text = element_text(size = 15),
    strip.text.x = element_text(size = 18),
    axis.title.x = element_text(size = 18)
  ) +
  scale_fill_manual(
    values = c(
      "arable" = "#CCBB44", "built.up.area" = "#EE6677",
      "Non.agricultural.unmanaged.green.space" = "#228833",
      "water" = "#4477AA", other = "#BBBBBB"
    )
  ) +
  facet_wrap(~site_removed, ncol = 2)
ggsave(
  plot = plt,
  filename = "../Results/figures/SI_figures/agrirural_jk_individual_loadings.png",
  width = 120,
  height = 220,
  units = "mm",
  dpi = 300
)
plt
```

>>>>

set_ggplot_theme <- function() {
  theme_set(
    theme_classic() +
      theme(
        text = element_text(family = "URWHelvetica", size = 18),
        legend.position = "none",
        # plot.title = element_text(hjust = 0.5),
        # axis.text.x = element_text(angle = 0,  hjust=1)
      )
  )
}

set_ggplot_theme()

knitr::opts_chunk$set(
  dev = "png",
  dpi = 300,
  collapse = TRUE,
  comment = "#>",
  fig.width = 12,
  fig.height = 8
)

@@

```{r, diff-p-sites}

urban_p <- urban_lu %>% select(site, p)
rural_p <- rural_lu %>% select(site, p)

urban_p$LU = "Urban"
rural_p$LU = "Agri-rural"

comb <- rbind(urban_p, rural_p) %>% mutate(p = 1-p)
comb_ar <- comb %>% filter(LU == "Agri-rural")
comb_u <- comb %>% filter(LU == "Urban")

plt <- ggplot(comb, aes(y = p, x = LU)) +
  geom_violin(fill="gray") +
  # geom_boxplot(width=0.05) +
  ylab("Waggle dance use") +
  xlab("Environment")

ggsave(
  plot = plt,
  filename = "../Results/figures/SI_figures/urban_rural_violin.png",
  dpi = 300
)

ggsave(
  plot = plt,
  filename = "../Results/figures/SI_figures/urban_rural_violin_nobox.svg",
  dpi = 300
)

res = chisq.test(comb_ar$p, comb_u$p)
res

@@

```{r, urban_jk_outlier_removed, message = FALSE, error = FALSE, warning = FALSE, echo = TRUE}

# full data fit
model_pls <- plsRbeta(
  p_transform ~ .,
  data = urban.pcadata,
  nt = ncol(urban.pcadata) - 1,
  model = "pls-beta",
  verbose = FALSE
)

print(model_pls)

plsdata <- data.frame(
  prop.scouts = model_pls$dataY,
  pc1 = model_pls$tt[, 1]
)
plsbetamodel <- betareg(
  prop.scouts ~ pc1,
  plsdata
)

@@

make_plots_func <- function(urban_jk_loadings) {
  plt <- ggplot(data = urban_jk_loadings, aes(
    x = landuse_type, y = loadings, fill = landuse_type
  )) +
    geom_point(aes(colour = landuse_type), size = 8) +
    geom_segment(aes(
      x = landuse_type, xend = landuse_type,
      y = 0, yend = loadings, colour = landuse_type, size = .1
    )) +
    geom_hline(
      yintercept = 0, color = "black"
    ) +
    annotate(
      "rect",
      ymin = -urban_cuttoff,
      ymax = urban_cuttoff,
      xmin = 0, xmax = Inf,
      alpha = 0.2
    ) +
    ylab("Correlation") +
    coord_flip() +
    theme_classic() +
    theme(
      axis.line.y = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      legend.position = "None",
      axis.title.x = element_text(size = 80),
      axis.text.x = element_text(size = 60)
    ) +
    scale_colour_manual(
      values = c(
        "sparse.residential" = "#EE6677",
        "railway" = "#CCBB44", "parks.allotments.cemeteries" = "#228833"
      )
    ) +
    facet_wrap(~site_removed, nrow = 1) +
    theme(
      strip.text = element_text(size = 80)
    )
  return(plt)
}

plt <- make_plots_func(urban_jk_loadings %>% filter(site_removed != "None"))

ggsave(
  plot = plt,
  filename = "../Results/figures/SI_figures/urban_jk_individual_loadings.png",
  width = 800,
  height = 400,
  units = "mm",
  dpi = 300
)

# bur_blo <- urban_jk_loadings %>% filter(site_removed %in% c("BLO", "BUR")) %>%
#   make_plots_func()

# ggsave(
#   plot = bur_blo,
#   filename = "../Results/figures/SI_figures/bur_blo_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

# cad_gil <- urban_jk_loadings %>% filter(site_removed %in% c("CAD", "GIL")) %>%
#   make_plots_func()

# ggsave(
#   plot = cad_gil,
#   filename = "../Results/figures/SI_figures/cad_gil_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

# hhs_hor <- urban_jk_loadings %>% filter(site_removed %in% c("HHS", "HOR")) %>%
#   make_plots_func()

# ggsave(
#   plot = hhs_hor,
#   filename = "../Results/figures/SI_figures/hhs_hor_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

# mak_mpa <- urban_jk_loadings %>% filter(site_removed %in% c("MAK", "MPA")) %>%
#   make_plots_func()

# ggsave(
#   plot = mak_mpa,
#   filename = "../Results/figures/SI_figures/mak_mpa_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

# swp_zsl <- urban_jk_loadings %>% filter(site_removed %in% c("SWP", "ZSL")) %>%
#   make_plots_func()

# ggsave(
#   plot = swp_zsl,
#   filename = "../Results/figures/SI_figures/swp_zsl_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

@@

make_plots_func2 <- function(rural_jk_loadings){
  plt <- ggplot(data = rural_jk_loadings, aes(
    x = landuse_type, y = loadings, fill = landuse_type
  )) +
    geom_point(aes(colour = landuse_type), size = 8) +
    geom_segment(aes(
      x = landuse_type, xend = landuse_type,
      y = 0, yend = loadings, colour = landuse_type, size = .1
    )) +
    geom_hline(
      yintercept = 0, color = "black"
    ) +
    annotate(
      "rect",
      ymin = -rural_cuttoff,
      ymax = rural_cuttoff,
      xmin = 0, xmax = Inf,
      alpha = 0.2
    ) +
    ylab("Correlation") +
    coord_flip() +
    theme_classic() +
    theme(
      axis.line.y = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank(),
      legend.position = "None",
      axis.title.x = element_text(size = 80),
      axis.text.x = element_text(size = 60)
    ) +
    scale_colour_manual(
      values = c(
        "arable" = "#228833", "built.up.area" = "#EE6677",
        "Non.agricultural.unmanaged.green.space" = "#CCBB44",
        "water" = "#4477AA"
      )
    ) +
    facet_wrap(~site_removed, nrow = 1) +
    theme(
      strip.text = element_text(size = 80)
    ) +
    xlab("PC1 Loadings")
  return(plt)
}

plt <- make_plots_func2(rural_jk_loadings %>% filter(site_removed != "None"))

ggsave(
  plot = plt,
  filename = "../Results/figures/SI_figures/rural_jk_individual_loadings.png",
  width = 800,
  height = 400,
  units = "mm",
  dpi = 300
)

# bel_bfi <- rural_jk_loadings %>% filter(site_removed %in% c("BEL", "BFI")) %>%
#   make_plots_func2()

# ggsave(
#   plot = bel_bfi,
#   filename = "../Results/figures/SI_figures/bel_bfi_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

# her_mel <- rural_jk_loadings %>% filter(site_removed %in% c("HER", "MEL")) %>%
#   make_plots_func2()

# ggsave(
#   plot = her_mel,
#   filename = "../Results/figures/SI_figures/her_mel_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

# sau_som <- rural_jk_loadings %>% filter(site_removed %in% c("SAU", "SOM")) %>%
#   make_plots_func2()

# ggsave(
#   plot = sau_som,
#   filename = "../Results/figures/SI_figures/sau_som_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

# sra_stu_yal <- rural_jk_loadings %>% filter(site_removed %in% c("SRA", "STU", "YAL")) %>%
#   make_plots_func2()

# ggsave(
#   plot = sra_stu_yal,
#   filename = "../Results/figures/SI_figures/sra_stu_yal_loadings.png",
#   width = 120,
#   height = 200,
#   units = "mm",
#   dpi = 300
# )

### 2023-05-02 inst/publication/Manuscript/paper.Rmd
Added AIC variation

landuse_area %>%
  arrange(Environment, desc(`% coverage`)) %>%
  mutate(`% coverage` = round(`% coverage`, digits = 1)) %>%
  flextable() %>%
  set_caption(
    "Percentage area covered for each land-use type in the agri-rural and urban environments in the sites studied."
  ) %>%
  set_table_properties(layout = "autofit")
```

>>>>

landuse_area %>%
  arrange(Environment, desc(`% coverage`)) %>%
  mutate(`% coverage` = round(`% coverage`, digits = 1)) %>%
  flextable() %>%
  set_caption(
    "Percentage area covered for each land-use type in the agri-rural and urban environments in the sites studied."
  ) %>%
  set_table_properties(layout = "autofit")

library(xtable)

landuse_area %>%
  arrange(Environment, desc(`% coverage`)) %>%
  mutate(`% coverage` = round(`% coverage`, digits = 1)) %>%

  xtable()

```

### 2023-05-02 inst/publication/Manuscript/supplementary_material.tex
Added AIC variation

\DeclareCaptionLabelFormat{sfig}{#1 S#2}
\captionsetup[figure]{labelformat=sfig}

@@

\title{Waggle dance distributions quantify collective foraging in honey bee colonies: Supplementary material}
%\author{}
\maketitle

@@

\captionof{table}{Fit results for the fitting of the waggle dance model to each site.}
\input{../results/figures/SI_figures/fittable.tex}

@@

\begin{figure}[h]
	\centering
	\includegraphics{../results/figures/SI_figures/allsites_plot.png}
	\caption{\textbf{Cumulative frequency distribution} of waggle dance durations and fits of the collective (red line) and individual (blue line) models for all 20 sites}
\end{figure}

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics{../results/figures/SI_figures/agrirural_jk_individual_loadings.png}
	\caption{\textbf{Loadings of PLS calculated for each site removed for the agri-rural sites}. Each plot shows the loadings of the first principle component with that site removed from the analysis, showing the individual points making up the overall box plot loadings in Fig 4b.}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics{../results/figures/SI_figures/urban_jk_individual_loadings.png}
	\caption{\textbf{Loadings of PLS calculated for each site removed for the urban sites}. Each plot shows the loadings of the first principle component with that site removed from the analysis, showing the individual points making up the overall box plot loadings in Fig 4d.}
\end{figure}

>>>>

\DeclareCaptionLabelFormat{sfig}{#1 S#2}
\DeclareCaptionLabelFormat{stab}{#1 S#2}
\captionsetup[figure]{labelformat=sfig}
\captionsetup[table]{labelformat=stab}

@@

\title{Honeybees vary communication and collective decision making across landscapes: Supplementary material}
%\author{}
\maketitle

@@

\captionof{table}{Fit results for the fitting of the waggle dance model to each site.}
\input{../Results/figures/SI_figures/fittable.tex}

@@

\begin{figure}[h]
	\centering
	\includegraphics{../Results/figures/SI_figures/allsites_plot.png}
	\caption{\textbf{Cumulative frequency distribution} of waggle dance durations and fits of the collective (red line) and individual (blue line) models for all 20 sites}
\end{figure}

@@

\clearpage

\captionof{table}{Percentage area covered for each land-use type in the agri-rural and urban environments in the sites studied.}
\begin{table}[ht]
	\centering
	\begin{tabular}{rllr}
		\hline
		Environment & Land-use & \% coverage \\ 
		\hline
		Agri-rural & Arable & 28.30 \\ 
		Agri-rural & Pasture & 23.30 \\ 
		Agri-rural & Woodland & 21.10 \\ 
		Agri-rural & Built Up Area & 15.00 \\ 
		Agri-rural & Fruit & 3.10 \\ 
		Agri-rural & Oilseed Rape & 2.90 \\ 
		Agri-rural & Non Agricultural Unmanaged Green Space & 2.80 \\ 
		Agri-rural & Non Agricultural Managed Green Space & 1.80 \\ 
		Agri-rural & Other Agricultural & 1.50 \\ 
		Agri-rural & Water & 0.20 \\ 
		Urban & Sparse Residential & 34.80 \\ 
		Urban & Continuous Central & 24.30 \\ 
		Urban & Dense Residential & 21.80 \\ 
		Urban & Parks Allotments Cemeteries & 7.90 \\ 
		Urban & Woodland & 4.20 \\ 
		Urban & Water & 3.40 \\ 
		Urban & Amenity Grassland & 2.60 \\ 
		Urban & Railway & 1.00 \\ 
		\hline
	\end{tabular}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics{../Results/figures/SI_figures/agrirural_jk_individual_loadings.png}
	\caption{\textbf{Loadings of PLS calculated for each site removed for the agri-rural sites}. Each plot shows the loadings of the first principle component with that site removed from the analysis, showing the individual points making up the overall box plot loadings in Fig 4b.}
\end{figure}

### 2023-05-02 inst/publication/README.Rmd
updated readme
Added AIC variation

This directory contains all the code and data needed to reproduce the article:

(insert article reference)

# Instructions

@@

The manuscript is an R-markdown document called `paper.Rmd`. This is rendered into a word document called `paper.doc`. The Supplementary material is a tex file, `supplementary_material.tex`.

>>>>

This directory contains all the code and data needed to reproduce the article: *Honeybees vary collective decision making in different landscapes*

## Instructions

@@
